Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-24 article/ms.tex
added conclusions and discussion points based off sims meetings, also Na dust picture

\begin{figure}
	\includegraphics[width=\columnwidth]{loggteffof113.png}
    \caption{Effective temperature, log surface gravity, metalicity. \todo{The large, random spread in $\logg$, $\teff$ and [Fe/H] implies that the candidates are simply stars which have formed from poluted material, rather than any special type of star such as red-clump giants.}}
    \label{tefflogg}
\end{figure}

@@

One possible scenario that could possibly produce a large K enhanced signature, as well as the observed Na pattern, throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star. The SAGB star produces K (destroying Na) which is then mixed into its envelope. It then deposits its K rich envelope onto its smaller companion through conventional binary accretion. This smaller and companion would continue to evolve long after the SAGB star is gone and, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, would not. If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}. In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants. Note that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.

This scenario allows for K abundances to appear at a range of metalicities, as this scenario could play out throughout the life of the Milky Way. It also  accounts for the significant minority population of the stars which show Na enhancements.

It does not, however, account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation. The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is unlikely to say the least.

A direct test of this scenario would be the determination of whether at least most of the sample are binaries with neutron star remnants.

@@

The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in a region(s) of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases. This interpretation is supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.

@@

Suppose some unknown event(s) that can only occur in very metal poor environments occurs. This event results in material depleted in Mg and enhanced in K.

The generation of stars that forms directly from this gas carries this signiature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419. We will label this generation of stars Generation 1.

When the most massive stars of Generation 1 die however, they release metals into the this gas, including Mg, which is easy to form, but \textit{not} K, which is difficult to form. The Mg depletion originally carried in this gas relative to the original levels of iron is much harder to detect in the next generation of stars forming from this material, Generation 2, as the original depleted signature is obscured by the influx of Mg from Generation 1. The K enhancement however remains relatively easy to detect, having only been reduced relative to iron by the total amount of iron released.

@@

If the [K/Fe] anti-correlation with [Fe/H] is physical, then the presmumed production of anomalously high amounts of K throughout the life of the Milky Way is turned on its head. Instead, it can be concluded that the origin of the Mg-K anti-correlation is confined to a certain epoch in the evolution of galaxies and globular clusters.

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

>>>>

\begin{figure}
	\includegraphics[width=\columnwidth]{loggteffof113.png}
    \caption{Effective temperature, log surface gravity, metalicity. \todo{The large, random spread in $\logg$, $\teff$ and [Fe/H] implies that the candidates are simply stars which have formed from poluted material, rather than any special type of star such as red-clump giants. Further, this distribution allays concerns that the sample is the result of some NLTE effect.}}
    \label{tefflogg}
\end{figure}

@@

One possible scenario that could possibly produce a large K enhanced signature, as well as the observed Na pattern, throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star. The SAGB star produces K (destroying Na) which is then mixed into its envelope. It then deposits its K rich envelope onto its smaller companion through conventional binary accretion. This smaller and companion would continue to evolve long after the SAGB star is gone and, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, would not. If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}. In this scenario, it is this smaller binary companion star that makes up our sample of 113 giant observations. Recall that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.

This scenario allows for K abundances to appear at a range of metalicities, as this scenario could play out throughout the life of the Milky Way. It also  accounts for the significant minority population of the stars which show Na enhancements, while allowing others to retain normal levels of [Na/Fe]. \todo{Check dust lanes.}

It does not, however, account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation. The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least. One might imagine however that the case of NGC 2808 might be accounted for by such a mechanism.

A direct test of this scenario would be the determination of whether at least most of the sample are binaries with O-Ne white dwarf remnants, which would indicate that they were indeed SAGB binaries once.

@@

The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in a region(s) of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases. This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.

@@

Suppose some unknown event(s) that can only occur in very metal poor environments occurs. This event results significant amounts of material depleted in Mg and enhanced in K.

The generation of stars that forms directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419. We will label this generation of stars Generation 1.

When the most massive stars of Generation 1 die however, they release metals into the this gas, including significant amounts of Mg which is formed in copious amounts in core collapse supernovae, but \textit{not} K, which is difficult to form. The Mg depletion originally carried in this gas relative to the original levels of iron is much harder to detect in the next generation of stars forming from this material, Generation 2, as the original depleted signature is obscured by the influx of Mg from Generation 1. The K enhancement however remains relatively easy to detect, having only been reduced relative to iron by the total amount of iron released.

@@

If the [K/Fe] anti-correlation with [Fe/H] is physical, then the presmumed production of anomalously high amounts of K throughout the life of the Milky Way may be turned on its head. Instead, it could concluded that the origin of the Mg-K anti-correlation is temporally confined to a certain epoch in the evolution of galaxies and globular clusters.

However, even if physical, there are still several outstanding issues in the above scenario.

First and most importantly, the extreme difficulty of forming the original cloud of Mg depleted, K enriched material in the first place must be emphasized. Primordial conditions (ie. pre-mystery-event) will contain some iron for the same reason that globular clusters are not at zero metalicity. This iron also comes with Mg; the only way to produce iron without Mg is Type Ia supernovae, which are not believed to be common in the early universe, and don't produce K anyway. There is no known process from which you can go from a massive cloud with galactic levels of [Mg/Fe], such as forms the Mg normal population in NGC 2419, to one with [Mg/Fe] levels of around -1.5 dex. Huge amounts of Fe rich material containing virtually no Mg would be required to be released into the cloud, and that's before even considering the difficulty of also producing K... and at the same time apparently sometimes (but not always) also producing Na.

The second issue with the scenario is that it would be expected that stars would form from the hypothetical cloud in groups, as compression events pass through the gas, triggering star formation. There is no evidence of such grouping in any of the data for the 113 star sample.

Another interpretation of the [K/Fe]-[Fe/H] anti-correlation could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metalicity of the star.

\section{Conclusions}
Of the 454180 giant sample from \lamost, 113 candidate stars were identified as likely to have enhanced K and depleted Mg based on absorption spectra. These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects. The candidate sample reflected the metalicity distribution of the base \textit{LAMOST} sample.

 Upon conducting abundance analysis, it was found that despite the searching for both Mg depletions and K enhancements, the sample of stars showed no definitive Mg depletion, although it did display anomalously high levels of K. None of the candidates had calculated abundances of Mg or K consistent with NGC 2419 or NGC 2808's extreme populations.

The sample was also found found to be bimodal in Na, with a significant minority population of stars showing enhanced Na well above galactic levels. Finally, an intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains questionable.
